---
title: "p8105_hw5_yh3094"
author: "Yun He"
date: "November 4, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
```

# Problem 1

## Create a tidy dataframe containing data from all participants

```{r study_data_clean, message=FALSE}
read_file_data = function(path){
  read_csv(str_c("./data/", path))
}

study_data = 
  tibble(file_name = list.files("./data")) %>% 
  mutate(data = purrr::map(file_name, read_file_data)) %>% 
  unnest() %>% 
  separate(file_name, c("control_arm", "subject_id"), sep = "_") %>% 
  mutate(subject_id = str_remove(subject_id, ".csv")) %>%
  gather(week, obs_value, week_1:week_8) %>% 
  mutate(week = str_remove(week, "week_"))
```

## Make a spaghetti plot showing observations on each subject over time

```{r plot_for_study}
study_data %>% 
  mutate(week = as.numeric(week)) %>%
  ggplot(aes(x = week, y = obs_value, color = subject_id)) +
  geom_line() +
  facet_grid(~control_arm)
```

Participants in the experimental arm seem to have higher observations than those in the control arm. In addition, participants in the experimental arm seem to have higher and higher observations over time, while this trend wasn't observed in the control arm. 

# Problem 2

## Import the homicide data

```{r homicide_data_import, message=FALSE}
homicide_data = 
  GET("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  content("raw") %>% 
  read_csv()
str(homicide_data)
```

Data on homicides contains `r nrow(homicide_data)` observations and `r ncol(homicide_data)` variables. Variable for `reported_date` is class `integer`. Variables for `latitude` and `longitude` are class `numeric`. And all other variables are class `character`. 

## Create a city_state variable and summarize

```{r homicide_data_clean}
homicide_data = homicide_data %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) 

## summarize within cities to obtain the total number of homicides
total_homicides = homicide_data %>% 
  group_by(city_state) %>% 
  summarise(n_homicides = n())
total_homicides

## summarize within cities to obtain the number of unsolved homicides
unsolved_homicides = homicide_data %>% 
  group_by(city_state) %>% 
  summarise(n_unsloved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))
unsolved_homicides

homicide = full_join(total_homicides, unsolved_homicides, by = "city_state")
homicide
```

## Data analysis of the city of Baltimore, MD

```{r baltimore}
baltimore = homicide %>% filter(city_state == "Baltimore, MD")
prop_test_balti = prop.test(baltimore$n_unsloved, baltimore$n_homicides)
tibble(
  city_state = "Baltimore, MD",
  estimated_prop = broom::tidy(prop_test_balti) %>% pull(estimate),
  conf_low = broom::tidy(prop_test_balti) %>% pull(conf.low),
  conf_high = broom::tidy(prop_test_balti) %>% pull(conf.high)
)
```

## Run the analysis in the whole dataset

```{r prop_test_for_whole}
prop_test_result = function(x, n){
  result = broom::tidy(prop.test(x, n))
  tibble(
    estimated_prop = result %>% pull(estimate),
    conf_low = result %>% pull(conf.low),
    conf_high = result %>% pull(conf.high)
  )
}

homicide %>% 
  mutate(prop_test_result = purrr::map2(n_unsloved, n_homicides, prop_test_result)) %>% 
  unnest()
```

## Create a plot that shows the estimates and CIs for each city 

```{r prop_test_plot}
homicide %>% 
  mutate(prop_test_result = purrr::map2(n_unsloved, n_homicides, prop_test_result)) %>% 
  unnest() %>% 
  mutate(city_state = fct_reorder(city_state, estimated_prop)) %>% 
  ggplot(aes(x = city_state, y = estimated_prop)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

